Review of Assigned Readings

### 2017-12-27 documentation/documentation.tex
created section hardware setup

\subsubsection{Hardware Setup}
(Severin's Part)

>>>>

\subsubsection{Hardware Setup}
As explained in the previous section the twitter API was used to filter tweets in realtime based on the buzzword "bitcoin". The python program was running for seven days without interruption (to be checked!!!!!!!!!!!) on a raspberry pi (rpi) which was accessed with a secure shell (SSH) connection. This approach allowed us to ensure a continuous data stream while being able to access the program output regardless anywhere and anytime. Furthermore due to a low energy consumption of the rpi the method is also the most cost efficient one compared to a personal computer or NAS Server. The following section describes the different steps that have been taken in order to setup the rpi, ssh, git and python3.\newline The following steps were conducted by using a Raspberry Pi 2, a micro SD card and Python3.

\paragraph{(1)Setup of the Raspberry Pi}\mbox{}\\
- Burn image 2017-11-29-raspbian-stretch.zip to micro SD card available from \newline https://www.raspberrypi.org/downloads/raspbian/ \newline
- Boot image from micro SD card \newline
- Open SSH session using PuTTY SSH client for Windows available from \newline https://www.chiark.greenend.org.uk/\~sgtatham/putty/latest.html \newline
- Login to server with credentials \newline

\paragraph{(3) Update system to the newest software}\mbox{}\\
- Update list of applications with the command: sudo apt-get update \newline
- Update applications with the command: sudo apt-get upgrade \newline

\paragraph{(4) Setup Git}\mbox{}\\
- Install git using the command: sudo apt-get install git \newline
- Clone git repository from https://github.com/joelsonderegger/twitterbitcoin.git \newline

\paragraph{(5) Setup Pyhton3}\mbox{}\\
- Install Python3 using the command: sudo apt-get install Python3 \newline
- Install the tweepy module for python using the command: pip install tweepy \newline

\paragraph{(6) Collect Twitter Data}\mbox{}\\
- Open a new screen using the command: screen -S 'name' \newline
- start python program using the command: python3 CollectTwitterData.py \newline
- Detach the screen to keep the program running after secure shell connection has been terminated using the commands: Ctrl+A , Ctrl+D \newline
- Re-attach the screen to check whether the script is still running using the command: screen -r 'name' \newline

\paragraph{(7) Download the collected data}\mbox{}\\
- Install FileZilla available https://filezilla-project.org/ \newline
- Connect to rpi and navigate to data location \newline
- Download data manually \newline \newline In summary, this approach worked quite well and run smoothly after all bugs have been resolved from the file CollectTwitterData.py A clean setup is crucial to ensure continuous data collection over a longer period.
